% Chapter 1: The Real Number
% Introduces some definitions that lead to the real numbers
% being defined

\chapter{The Real Numbers}

\setcounter{section}{1}

%%% 1.2 %%%
\section{Some Preliminaries}

\bx{
\ea{
	\item 
	\begin{proof}
		AFSOC $\sqrt{3}$ is rational, so $\exists m, n \in \mathbb{Z}$ such that 
		\begin{equation*}
			\sqrt{3} = \frac{m}{n},
		\end{equation*}
		where $\frac{m}{n}$ is in lowest reduced terms.
		Then we can square both sides, yielding $3 = \pa{\frac{m}{n}}^2 \lra 3n^2 = m^2$. Now, we know $m^2$ is a multiple of 3 and thus $m$ must also. Then, we can write $m = 3k$, and derive
		\begin{align*}
		(\sqrt{3})^2 &= \pa{\frac{3k}{n}}^2 \\
		3n^2 &= 9k^2 \\
		n^2 &= 3k^2
		\end{align*}
		Similar to before, we come to the conclusion that $n$ is a multiple of 3. However, this is a contradiction since $m, n$ are both multiples of 3 and we assumed $\frac{m}{n}$ was in lowest terms. Thus, we conclude $\sqrt{3}$ is irrational.
	\end{proof}
	The same proof for $\sqrt{3}$ works for $\sqrt{6}$ as well.

	\item We cannot conclude that $\sqrt{4} = \frac{m}{n}$ implies that 
	$m$ is a multiple of $4$, since we have 
	\begin{equation*}
		4n^2 = m^2 \quad \Rightarrow \quad 2n = m,
	\end{equation*}
	so we cannot reach our contradiction that $m/n$ is not in lowest terms.
}
}


\bx{
\ea{
	\item False. Consider 
	\begin{equation*}
		A_n = \left[0, \frac{1}{n}\right).
	\end{equation*}
	Then 
	\begin{equation*}
		\bigcap_{n=1}^\infty A_n = \{0\}.
	\end{equation*}
	\item True. Since $\forall i, A_i \subseteq A_1$, $\exists x$ such that $\forall i, x \in A_i$.
	Therefore, the intersection cannot be empty. Then, every set is finite, and the intersection of 
	any number of finite sets will be finite.
	\item False. Consider $A = \{1, 2\}, B = \{1\}, C = \{2, 3\}$.
	\begin{equation*}
		\{1, 2\} \cap \pa{
			\{1\} \cup  \{2, 3\}
		} = \{1, 2\}
		\neq \pa{
			\{1, 2\} \cap \{1\}
		} \cup \{2, 3\}
		= \{1, 2, 3\}
	\end{equation*}
	\item True. Intersection is associative.
	\item True. Intersection is distributive over union.
	\begin{proof}
		We will prove 
		\begin{equation}
			A \cap \pa{B \cup C} = \pa{A \cap B} \cup \pa{A \cap C}
			\label{eq:set_distributive}
		\end{equation}
		by set inclusion. 

		\begin{itemize}
			\item Suppose $x \in A \cap \pa{B \cup C}$. By the definition of intersection,
			we know $x \in A$ and $x \in B \cup C$, the latter which means $x \in B$ or $x \in C$.
			
			We can consider 2 cases for $x$,

			\begin{enumerate}[label=\arabic*.]
				\item $x \in B$. Then we know  $x \in A$ and $x \in B$, so $x \in A \cap B$ and therefore $x \in \pa{A \cap B} \cup \pa{A \cap C}$ 
				\item $x \in C$. Symmetric to the case above.
			\end{enumerate}

			in all cases, we see $x \in A \cap \pa{B \cup C}$ implies $x \in \pa{A \cap B} \cup \pa{A \cap C}$, so 
			\begin{equation*}
				A \cap \pa{B \cup C} \subseteq \pa{A \cap B} \cup \pa{A \cap C}
			\end{equation*}

			\item Suppose $x \in \pa{A \cap B} \cup \pa{A \cap C}$.
			Then we have two cases
			\begin{enumerate}[label=\arabic*.]
				\item $x \in A \cap B$. This means $x \in A$ and $x \in B$. If $x \in B$, then $x \in B \cup C$, since $B \subseteq B \cup C$.
				Putting these facts together, we see $x \in A \cap \pa{B \cup C}$.
				\item $x \in A \cap C$. Symmetric to the case above.
			\end{enumerate}
			in all cases, we see $x \in \pa{A \cap B} \cup \pa{A \cap C}$ implies $x \in A \cap \pa{B \cup C}$, so 
			\begin{equation*}
				\pa{A \cap B} \cup \pa{A \cap C} \subseteq A \cap \pa{B \cup C} 
			\end{equation*}
		\end{itemize}
	\end{proof}
}
}

\bx{
\ea{
	\item If $x \in \pa{A \cap B}^c$, then we have cases
	\begin{itemize}
		\item $x \in B$ and $x \not\in A$. Then $x \not\in A$ implies $x \in A^c \Rightarrow x \in A^c \cup B^c$.
		\item $x \in A$. Symmetric to above.
		\item $x \not\in A$ and $x \not\in B$. Then $x \in A^c$ so $x \in A^c \cup B^c$.
	\end{itemize}
	
	\item If $x \in A^c \cup B^c$, then we have cases
	\begin{itemize}
		\item $x \in A^c$. Then $x \not\in A$ so $x$ cannot be in the intersection of $A$ and $B$, so 
		$x \in \pa{A \cap B}^c$.
		\item $x \in B^c$. Symmetric to above.
	\end{itemize}
	\item Proof for $\pa{A \cup B}^c = A^c \cap B^c$ pretty similar to above.
}
}

\bx{
We are verifying the triangle inequality with $a, b$.
\ea{
	\item If $a, b$ have the same sign, then 
	\begin{align*}
		\abs{a + b} &= a+b\\
		\abs{a} + \abs{b} &= a + b\\
		\Rightarrow\, \abs{a+b} &= \abs{a} + \abs{b}\\
		\Rightarrow\, \abs{a+b} &\leq \abs{a} + \abs{b}
	\end{align*}

	\label{ex_triangle_ineq_same_sign}

	\item 
	\begin{itemize}
		\item $a \geq 0, b < 0$.
		\begin{align*}
			\abs{a + b} 
			&\leq \abs{a}\\
			&\leq \abs{a} + \abs{b}
		\end{align*}

		\item $a + b \geq 0$.
		At most one of $a, b$ is negative. If they are both positive, then 
		we have already shown this in part \ref{ex_triangle_ineq_same_sign}.
		Otherwise, WLOG $a$ is negative. Then 
		\begin{align*}
			\abs{a + b} 
			&\leq \abs{b}\\
			&\leq \abs{a} + \abs{b}
		\end{align*}
	\end{itemize}
}
}

\bx{
\ea{
	\item Substitute in $b' = -b$ into the triangle inequality.
	\item Easy to prove directly without using triangle inequality. \TODO.
	
	A direct proof will look something like:
	\begin{itemize}
		\item If $a, b$ are the same sign, then equality holds 
		\item If $a, b$ are different signs, then if $b$ is negative, then $\abs{a-b} = \abs{a} + \abs{b}$, 
		and if $a$ is negative, then $\abs{a-b} = \abs{a} + \abs{b}$, both of which bound $\abs{\abs{a} - \abs{b}}$.
	\end{itemize}
}
}

\bx{
\ea{
	\item Yes, since $f\pa{A \cap B} = [1, 4] = [0, 4] \cap [1, 16] = f(A) \cap f(B)$. This is by coincidence though, as we will later see.
	Yes, since $f\pa{A \cup B} = [0, 16] = [0, 4] \cup [1, 16] = f(A) \cup f(B)$.
	\item Choose $A = [-2, 0], B = [0, 2]$
	\item Suppose $x \in g(A\cap B)$, then $\exists x' \in A \cap B$ such that $g(x') = x$.
	Since $x' \in A$ and $x' \in B$, we know $x = g(x') \in g(A), g(B)$, so we conclude $x \in g(A) \cap g(B)$.
	\item Equality. \TODO too lazy to write out the proof. Similar to above.
}
}

\bx{
\ea{
	\item \TODO I don't think we want to include $x \in \mathbb{I}$...
	\begin{align}
		f^{-1}(A) &= [0, 2]\\
		f^{-1}(B) &= [0, 1]
	\end{align}
	We see $f^{-1}(A\cap B) = f^{-1}(A) \cap f^{-1}(B)$ in this case.
	$f^{-1}(A\cup B) = f^{-1}(A) \cup f^{-1}(B)$ is also true.
	\item \TODO
}
}

\bx{
Negating statements. Took some liberties. Also notice that these statements are not necessarily true.
\ea{
	\item There exists a real number satisfying $a < b$, such that $\forall n \in \mathbb{N}$, $a+1/n \geq b$.
	\item There exists two distinct real numbers such that there is not a rational number between them.
	\item There exists a natural number $n \in \mathbb{N}$ such that $\sqrt{n}$ is not a natural number nor an irrational number.
	\item  There exists a real number $x \in \mathbb{R}$ such that $\forall n \in \mathbb{N}$, $n \leq x$.
}
}

\bx{
We are given the sequence 
\begin{equation}
	x_1 = 1, x_{n+1} = \frac{1}{2}x_{n} + 1
\end{equation}
and want to show $\forall i \geq 1, x_i < 2$.

We can show this with a direct proof of summation.

An alternative that the book probably wants to see is using \textbf{induction}.

\begin{itemize}
	\item Base Case: $x_1 = 1 < 2$
	\item Inductive case. Assume $\forall i < n+1, x_i < 2$. Then $x_i/2 + 1 < 2$ since $x_i/2 < 1$.
	\item By induction our original claim is proved.
\end{itemize}
\label{ex:induction_1_2_9}
}

\bx{
\ea{
	\item Similar to Exercise \ref{ex:induction_1_2_9}. $y_n < 4$ means $(3/4)y_n < 3$ so $(3/4)y_n + 1 < 4$
	\item In brief,
	\begin{align}
		y_n &\leq \frac{3}{4}y_n + \frac{1}{4}y_n\\
		&< \frac{3}{4}y_n + 1 \tag{Using $y_n < 4$}\\
		&< y_n+1 \tag{Sequence definition}
	\end{align}
}
}

\bx{
	A combinatorial argument is that in order to construct a set, we have 2 choices for every element, 
	to include it or not to. Therefore, we have 
	\begin{equation*}
		\prod_{i=1}^n 2 = 2^n
	\end{equation*}
}

\bx{
\ea{
	\item We know that $\pa{A_1 \cup A_2}^c = A_1^c \cap A_2^c$. So if we are trying to show 
	$\pa{A_1 \cup A_2 \cup A_3}^c = \pa{A_1 \cup A_2}^c \cap A_3^c = A_1^c \cap A_2^c \cap A_3^c$.
	Induction lets us apply the property on smaller parts of our expression.
	\item Induction only proves the property for some $n \in \mathbb{N}$, i.e. some finite $n$. It is not shown for an infinite $n$.
	\item \TODO. Sketch: If $x$ is not in the union of all the $A_n$, then $x$ cannot be part of any particular $A_n$ either, or else it would be in the union.
}
}

%%% 1.3 %%%
\section{The Axiom of Completeness}
\setcounter{exercise}{0}

\bx{
\ea{
	\item We compute the additive inverse for each element in $\mathbb{Z}_5$. 
	\begin{align*}
		0 + 0 &\equiv 0 \\
		1 + 4 &\equiv 0 \\
		2 + 3 &\equiv 0 \\
		3 + 2 &\equiv 0 \\
		4 + 1 &\equiv 0
	\end{align*}
	\item We compute the multiplicative inverse for each element in $\mathbb{Z}_5$. 
	\begin{align*}
		1 \times 1 &\equiv 1 \\
		2 \times 3 &\equiv 1 \\
		3 \times 2 &\equiv 1 \\
		4 \times 4 &\equiv 1
	\end{align*}
	\item $\mathbb{Z}_4$ is not a field because multiplicative inverses do not exist for every single element.
	For example, $2$ multiplied with any number is even, which cannot $\equiv 1 \pmod{4}$.

	We conjecture that $\mathbb{Z}_n$ always has additive inverses and only has multiplicative inverses if $n$ is prime.
}
}

\bx{
We are writing a formal definition for the \textit{infimum} of a set.
\ea{
	\item  $s = \inf A$ means 
	\begin{enumerate}[label=\roman*)]
		\item $s$ is a lower bound for $A$
		\item if $b$ is any lower bound for $A$, then $b \leq s$
	\end{enumerate}
	\item If $s\in \mathbb{R}$ is a lower bound for $A \subseteq \mathbb{R}$, then $s=\inf A$ iff $\forall \epsilon > 0, \exists a \in A$ such that $s + \epsilon > a$.
	\begin{proof}
		($\Rightarrow$)
		If $s=\inf A$, then $s$ is the greatest lower bound for $A$,
		meaning any $s+ \epsilon$ for $\epsilon > 0$ will be greater than some element of $A$,
		otherwise $s+ \epsilon$ is a greater lower bound and leads to a contradiction that$s \neq \inf A$.
		
		($\Leftarrow$) 
		If $\forall \epsilon > 0, \exists a \in A$ such that $s+\epsilon > a$,
		then since $s$ is a lower bound, $\forall b > s$, $b$ will not be a lower bound for $A$
		since if, $b > s$, then we can choose $\epsilon = b-s > 0$, and we know that 
		$\exists a \in A$ where $a < s + \epsilon < b$, which means $b$ is not a lower bound. 
		Thus, all lower bounds $b$ must be such that $b \leq s$,
		and we conclude $s = \inf A$.
	\end{proof}
}
}

\bx{
\ea{
	\item Since $\inf A$ is a lower bound for $A$, we know $\inf A \in B$.
	Now, we need to show $\inf A$ is the supremum of $B$. 
	$\inf A$ is the least upper bound for $B$, since if $\exists b \in B, b > \inf A$,
	then we know that this $b$ is not a lower bound for $A$, so no such $b$ exists.
	\item There might be a typo in this question. I think the question was meant to read 
	``explain why there is no need to assert that the greatest \textit{lower bound} in the Axiom of Completeness.'' 
	In this case, the answer would be that the Axiom of Completeness already implies the greatest lower bound property,
	so there is no need to explicitly state it.
	\item We can take the negative of all elements in $A$, find $\sup A$, and then negate again to get $\inf A$.	
}
}

\bx{
If $B \subseteq A$, then 
\begin{align*}
	\sup A = 
	s &\geq a, \forall a \in A \\
	s &\geq b, \forall b \in B \tag{since $B\subseteq A$} \\
	\Rightarrow\, s &\geq \sup B \tag{since $s$ is an upper bound for $B$}.
\end{align*}
}

\bx{
\ea{
	\item \begin{align*}
	&s = \sup(c + A) \\
	\Rightarrow\, &s \text{ is the least upper bound for } c + A \\
	\Rightarrow\, &s - c \text{ is the least upper bound for } A \\
	\Rightarrow\, &s - c = \sup A \\
	&s = c + \sup A
	\end{align*}

	\item \begin{align*}
		&s = \sup(cA) \\
		&\Rightarrow\, s \text{ is the least upper bound for } cA \\
		&\Rightarrow\, \frac{s}{c} \text{ is the least upper bound for } A \\
		&\Rightarrow\, \frac{s}{c} = \sup A \\
		&s = c \sup A
	\end{align*}
	\item If $c < 0$, $\sup(cA) = -c\inf(A)$.
}
}

\bx{
\ea{
	\item $\sup: 3; \inf: 1$
	\item $\sup: 1; \inf: 0$
	\item $\sup: \frac{1}{2}; \inf: \frac{1}{3}$
	\item $\sup: 9; \inf: \frac{1}{9}$
}
}

\bx{
If $a \geq a', \forall a' \in A$, and $a \in A$, then
\begin{equation}
	\forall \epsilon > 0, a - \epsilon < a,
\end{equation}
so $a$ is the least upper bound for $A$, and $a = \sup A$.
}

\bx{
Let \begin{equation}
	\epsilon = \sup B - \sup A > 0.
\end{equation}
since $s_b = \sup B$, $\exists b \in B \mid b > s_b - \epsilon / 2$. Since $s_b - \frac{\epsilon}{2} > \sup A$, then $b \geq \sup A$, so this $b \in B$ is an upper bound for $A$.	
}

\bx{
\ea{
	\item True, take the largest element in the set as the supremum.
	\item False, $\sup (0, 2) = 2$, but $2 > a \in (0, 2)$, but $\sup A = 2 \not < 2 = L$.
	\item False $A = (0, 2), B = [2, 3)$. We have that $\sup A = \inf B$
	\item True.
	\item False, take $A = B = (0, 2)$.
}
}

%%% 1.4 %%%
\section{Consequences of Completeness}
\setcounter{exercise}{0}

\bx{
If $a<0$, then we have two cases,
\begin{enumerate}
	\item If $b > 0$, then $a < 0 < b$.
	\item If $b = 0$, then we can take $-b, -a$, which satisfies $0 \leq -b < -a$, and apply Theorem 1.4.3.
\end{enumerate}
}


\bx{
\ea{
\item If $a, b \in \mathbb{Q}$, then 
\begin{align*}
	a &= \frac{a_1}{a_2} \\
	b &= \frac{b_1}{b_2} \\
	\lra a + b &= \frac{a_1b_2 + a_2b_1}{a_2b_2} \in \mathbb{Q}
\end{align*}
\item We can use contradiction, 
\begin{itemize}
	\item \AFSOC $a + t \in \mathbb{Q}$. Let $a+t = \frac{m}{n}$.
	We know $a = \frac{a_1}{a_2}$ since $a \in \mathbb{Q}$, so 
	\begin{align*}
		a + t &= \frac{m}{n}\\
		t &= \frac{m}{n} - \frac{a_1}{a_2} \in \mathbb{Q},
	\end{align*}
	which is a contradiction since we are given $t \in \mathbb{Q}$.
	Therefore, we conclude $a + t \in \mathbb{I}$.

	\item \AFSOC $at \in \mathbb{Q}$. 
	Let $at = \frac{m}{n}$.
	We know $a = \frac{a_1}{a_2}$ since $a \in \mathbb{Q}$, so 
	\begin{align*}
		at &= \frac{m}{n}\\
		t &= \frac{m}{n}\cdot\frac{a_2}{a_1} \in \mathbb{Q},
	\end{align*}
	which is a contradiction since we are given $t \in \mathbb{Q}$.
	Therefore, we conclude $at \in\mathbb{I}$
\end{itemize}

\item $\mathbb{I}$ is not closed under addition or multiplication.
\begin{align*}
	\pa{3 - \sqrt{2}} + \pa{3 + \sqrt{2}} &= 6 \not\in \mathbb{I}\\
	\pa{3 - \sqrt{2}} \cdot \pa{3 + \sqrt{2}} &= 5 \not\in \mathbb{I}
\end{align*}
}
}

\bx{
	We can apply Theorem 1.4.3, to find $a < q < b, q \in \mathbb{Q}$,
	and then subtract an irrational number such as $\sqrt{2}$ to end up at 
	\begin{equation}
		a - \sqrt{2} < q - \sqrt{2} < b - \sqrt{2},
	\end{equation}
	where $q- \sqrt{2} \in \mathbb{I}$.
}

\bx{
Suppose $\exists b$ lower bound such that $b > 0$. 
Then by Archimedean Property of $\mathbb{R}$, $\exists n \in \mathbb{N}$
such that $\frac{1}{n} < b$, which means $b$ is not a valid lower bound.
Thus $b \leq 0$, and 0 is a valid lower bound so the $\inf$ is 0.
}

\bx{
\AFSOC $\exists \alpha \in \bigcap_{n=1}^\infty (0, \frac{1}{n})$.
Then $\alpha >0$, but by Archimedean property of reals,
we have that $\exists n \in \mathbb{N} \mid \frac{1}{n} < \alpha$.
Since $\alpha \not\in \pa{0, \frac{1}{n}}$ leads to
$\alpha \not\in \bigcap_{n=1}^\infty (0, \frac{1}{n})$, 
a contradiction, we conclude the set is empty.
}

\bx{
\ea{
\item If $\alpha^2 > 2$, then 
\begin{align*}
	\pa{a - \frac{1}{n}}^2 &= \alpha^2 - \frac{2\alpha}{n} + \frac{1}{n^2} \\
	&> \alpha^2 - \frac{2\alpha}{n}
\end{align*}
choose $\frac{1}{n_0} < \frac{\alpha^2 - 2}{2\alpha}$. Then
\begin{align*}
	\pa{a - \frac{1}{n_0}}^2 &> \alpha^2 - \frac{2\alpha}{2\alpha}(\alpha^2 - 2)\\
	&> 2
\end{align*}
but $\alpha - \frac{1}{n_0} < \alpha$, so $\alpha$ is not
the least upper bound for the se, so $\alpha \neq \sup T$.
\item Just replace $\sqrt{2}$ with $\sqrt{b}$ for the proof above.
}
}

\bx{
Once we have assigned $g(i) = f(n_i)$, remove $f(n_i)$ from $A$.
Now, there is a new $n_{i+1} = \min\{n \in \mathbb{N}:f(n) \in A\setminus \{f(1), f(2), \dots, f(n_i)\}\}$.
Assign $g(i+1) = f(n_{i+1})$, and repeat.
}

\bx{
\ea{
\item If both are finite, then their union is finite and trivially countable. If one is finite, then first enumerate elements of the finite set. Then map the rest of $\mathbb{N}$ to the countably infinite set. If both are countably infinite, map one set to odds and the other to evens.
\item Induction only holds for finite integers, not infinity.
\item We can arrange each $A_n$ into row $n$ of a $\mathbb{N}\times \mathbb{N}$ matrix. Then, we enumerate by diagonalization.
}
}

\bx{
\ea{
\item If $A \sim B$, then there is a 1-to-1 mapping. We can just take the inverse of the mapping to derive $B \sim A$.
\item If we have $f: A \rightarrow B$, $g: B \rightarrow C$, then we can compose the functions so $g(f(x)): A \rightarrow C$.
}
}

\bx{
The set of all finite subsets of $\mathbb{N}$ can be ordered in increasing order by the sum of each subset.
}

\bx{
\ea{
	\item $f(x) = (x, 0.5) \in S$
	\item Interweave the decimal expansion of $x, y$, e.g. 
	\begin{equation}
		f(x, y) = 0.x_1y_1x_2y_2x_3y_3\dots
	\end{equation}
}
}

\bx{
\ea{
\item \begin{align*}
	\sqrt{2}&:x^2 -2 = 0 \\
	\sqrt[3]{2}&:x^3 - 2 = 0
\end{align*}
$\sqrt{3} + \sqrt{2}$ is not as trivial, so we will do it out in more steps.

There are two approaches to finding the integer coefficient polynomial. One is to take advantage of symmetry, and derive that 
\begin{equation}
\prod (x - (\pm \sqrt{3} \pm \sqrt{2})
\label{eq:chap1_sym}
\end{equation}
will work (using loose notation of course). A more general technique is to notice that 
\begin{align*}
	x &= \sqrt{3} + \sqrt{2} \\
	x^2 &= 5 + 2\sqrt{6} \\
	(x^2 - 5)^2 &= 24 \\
	x^4 - 10x^2 + 1 &= 0.
\end{align*}
Notice that this is actually the exact same answer we get in (\ref{eq:chap1_sym}) if you work it out.
\item Each element of $A_n$ is a root of a $n$ degree polynomial, which we can represent 
as an $(n+1)$-tuple of coefficients $\in \mathbb{Z}$. Therefore, $\abs{A_n} = k\abs{\mathbb{N}^{n+1}} = \abs{\mathbb{N}^{n+1}}$,
which we know is countable.
\item We proved earlier in Theorem 1.4.13 that a countably infinite union of countable sets is countable. Since there are a countable number of algebraic numbers, and reals are uncountable, we conclude that transcendentals are also uncountable.
}
}

\bx{
We are proving the \textbf{Schro\"{o}der-Bernstein Theorem}, which states if 
there exist 1-to-1 functions $f:X\rightarrow Y$ and $g: Y \rightarrow X$, then 
there exists a 1-to-1, onto function $h: X \rightarrow Y$, which implies $X \sim Y$.
\ea{
\item By the definition of 1-to-1, there must be a unique $x \in X$ such that $f(x) = y$.
A 1-to-1 function maps distinct elements from the domain to distinct elements of the range, so if we 
take the inverse $f^{-1}$, it will still be 1-to-1, this time from $Y\rightarrow X$.
\label{problem_1_4_13:parta}

\item Possibilities:
\begin{itemize}
	\item Zero: $g^{-1}$ is not guaranteed to be onto, it may not have an inverse for $x$.
	\item Finite: $g^{-1}(x)$ could exist, and similarly for $f^{-1}$. Once the element doesn't exist in the inverse domain,
	the chain will stop.
	\item Infinite: $x$ is in the range of $g$ and the domain of $f$
\end{itemize}
\label{problem_1_4_13:partb}

\item We have 2 cases 
\begin{itemize}
	\item The chains are disjoint. Nothing to prove here.
	\item The chains are not disjoint, i.e. they have one common element. Let us call this element $x$.
	We know to the right of $x$, all the elements in the two chains will be equal.
	From the left of $x$, the elements must be equal as well. 
	This is because the inverse chain must be unique starting from $x$, see part \ref{problem_1_4_13:parta}.
	Since all the elements are the same, the chains must be the same as well.
\end{itemize}

\item Since we know this chain started with $x\in X$, this $y$ could not have been created from the RHS,
otherwise this $y$ would be in the range of $f$. 
Therefore, this chain either has infinite or a finite of elements to the right.
\begin{itemize}
	\item Finite: the chain must start with an element $y \not\in Y$ but not in $f$'s range.
	This is because if we start with $x \in X$, then as mentioned before, all elements $y' \in Y$ will
	be in $f$'s range.
	Therefore, if we start with $y\in Y$, it will match the form indicated.
	\item  Infinite: The chain could not have an infinite elements to the left, because then 
	every $y$ must have come from an $f(x')$ for some $x' \in X$.
\end{itemize}
Therefore, these chains only can have a finite number of elements to the left, and it matches the 
form indicated.

\item By the definition of $C_x$, all the elements of $y \in C_x$ that are $\in Y$ 
are mapped by $f$ from $x \in X_1$. This means $f$ maps $X_1$ onto $Y_1$. Similar logic can 
be used for $g$ mapping $Y_2$ onto $X_2$.

Since we know $f$ is a 1-to-1 function from $X$ to $Y$, and we just showed it maps $X_1$ to $Y_1$.
We can conclude that $X_1 \sim Y_1$, since $f$ is a bijection between $X_1$ and $Y_1$.
We can similarly conclude $X_2 \sim Y_2$ with $g$.
Since $X_1, X_2$ are a partition of $X$, since all the chains are disjoint, and similarly for $Y_1, Y_2$ of $Y$, and there exists a bijection 
$f, g$ for $X_1 \sim Y_1$ and $X_2 \sim Y_2$ respectively, we conclude there must be a bijection between $X$ and $Y$.
Therefore, we conclude $X \sim Y$.

\begin{figure}[H]
	\centering
	\def\ellipseX{1}
	\def\ellipseY{2}
	\begin{tikzpicture}
		\draw (0, 0) ellipse ({\ellipseX} and {\ellipseY});
		\draw (\ellipseX+2, 0) ellipse ({\ellipseX} and {\ellipseY});
		\draw (0, \ellipseY) node[above] {$X$};
		\draw (\ellipseX+2, \ellipseY) node[above] {$Y$};
		\draw (-\ellipseX, 0) -- (\ellipseX, 0);
		\draw (2, 0) -- (2*\ellipseX+2, 0);
		\draw[<->] 
			(0, \ellipseY/2) node[below] {$X_1$} -- 
			(\ellipseX+2, \ellipseY/2) node[below] {$Y_1$} 
			node[midway, above] {$f$}
		;
		\draw[<->] 
			(0, -\ellipseY/2) node[above] {$X_2$} -- 
			(\ellipseX+2, -\ellipseY/2) node[above] {$Y_2$} 
			node[midway, above] {$g$}
		;
	\end{tikzpicture}
	\caption{$f$ and $g$ mapping $X$ and $Y$}
	\label{fig:problem_1_4_13_bijection}
\end{figure}
}
}

%%% 1.5 %%%
\section{Cantor's Theorem}
\setcounter{exercise}{1}

\bx{
\ea{
	\item Because $b_1$ differs from $f(1)$ in position 1
	\item $b_i$ differs from $f(i)$ in position $i$.
	\item We reach a contradiction that we can enumerate all the elements of $(0, 1)$,
	since we found a real number that isn't enumerated, and thus $(0, 1)$ is uncountable.
}
}

\bx{
\ea{
	\item $\frac{\sqrt{2}}{2} \in (0, 1)$ but is irrational
	\item We can just define our decimal representations to never have an infinite string of 9s.
}
}

\bx{
\AFSOC $S$ is countable. We will use a diagonalization proof.
Then we can enumerate the elements of $S$ using the natural numbers. Now, consider some $s = (s_1, s_2, \dots)$, where
\begin{equation}
	s_i = \begin{cases}
		0, \text{if } f(i), \text{position } i = 1\\
		1, \text{otherwise}
	\end{cases}
\end{equation}
Then since $s \neq f(i) \forall i$, we see $s \not \in S$. 
But this is a contradiction since $s$ only contains elements 0 or 1, and thus should be in $S$. 
Thus, we conclude that $S$ is uncountable.
}

\bx{
\ea{
	\item \begin{equation}
	\mathcal{P}(A) = \{\emptyset, \{a\}, \{b\}, \{c\}, \{a,b\}, \{a,c\}, \{b,c\}, \{a,b,c\}\}
	\end{equation}
	\item Each element has two choices when constructing a subset of $A$.
	To be, or not to be
	\footnote{sorry, had to do it. \textit{Addendum} For context, I took a Shakespeare class in college two semesters prior to when I first wrote this.},
	in the set.
}
}

\bx{
\ea{
	\item Many different answers.
	\begin{align*}
		&\{(a, \{a\}), (b, \{b\}), (c, \{c\})\} \\
		&\{(a, \emptyset), (b, \{b\}), (c, \{c\})\} \\
	\end{align*}
	\item \begin{equation*}
	\{(1, \{1\}), (2, \{2\}), (3, \{3\}), (4, \{4\})\}.
	\end{equation*}
	\item Because in general, $\abs{\mathcal{P}(A)} > \abs{A}$ for any set $A \neq \emptyset$.
	The intuition is that the power set has strictly more elements than $A$, so $A$ cannot map $\mathcal{P}(A)$ onto.
}
}

\bx{
	\begin{enumerate}
		\item $B = \emptyset$
		\item $B = \{a\}$
	\end{enumerate}
}

\bx{
\ea{
	\item \AFSOC $a' \in B$. Then that means $a \not \in f(a')$ by the definition of $B$. 
	But this is a contradiction since $a' \in B = f(a')$.
	\item \AFSOC $a' \not\in B = f(a')$. Then since $a' \not\in f(a')$, by the construction of $B$, 
	this implies $a' \in B$, but that is a contradiction from our original assumption.
}
}

\bx{
\ea{
	\item This is the same as $\mathbb{N} \times \mathbb{N}$, which is countable.
	\item Uncountable, since this is essentially constructing the power set of $\mathbb{N}$,
	and we know $\mathcal{P}(\mathbb{N})$ is uncountable.
	\item Is this question asking for the number of antichains or if there is an antichain with uncountable cardinality? 
	
	The latter is obvious, and \textit{no} is the answer since any subset of $\mathbb{N}$ is countable. 
	
	If we want to count the number of antichains, we notice that an antichain is essentially a partition of some subset of $B$.
	We also notice that every element of $\mathcal{P}(B)$ is also technically a partition, just a partition of one. This means that
	the cardinality of the set of antichains is at least the cardinality of $\mathcal{P}(B)$.
	If $B = \mathbb{N}$, then we know $\mathcal{P}(\mathbb{N})$ is already uncountable, so the set of antichains 
	will also be uncountable.
}
}
